\huge Tor's Usability for Censorship Circumvention

### 2016-04-23 pets2017-paper/pets2017-paper.tex
Fix the counts per environment in Study 1.
It said, "5 participants for each of the three censorship environments
E1, E2, and E3," which doesn't add up to 16. I got the counts from
sessions/pre/participant-summaries.txt:

E1: P2, P3, P4, P9, P10
E2: P7, P8, P11, P12, P13
E3: P1, P5, P6, P14, P15, P16

\subsection{Recruitment}
Using established practices from the field of user experience research~\cite{howmanyusers},
we recruited 5 participants for each of the three censorship environments E1, E2, and E3.
We pre-screened~\cite{screening} our participants for diversity of gender, age, technical expertise,
and self-reported familiarity with Tor in each simulated censorship environment for our summative
usability test~\cite{summative}.

>>>>

\subsection{Recruitment}
Using established practices from the field of user experience research~\cite{howmanyusers},
we recruited 16 participants across the three censorship environments:
5~in E1, 5~in E2, and 6~in E3.
We pre-screened~\cite{screening} our participants for diversity of gender, age, technical expertise,
and self-reported familiarity with Tor in each simulated censorship environment for our summative
usability test~\cite{summative}.
